Algebraic Principles for Concurrency Verification Tools

### 2013-10-03 Paper/paper.tex
More paper bits

\DeclareFontFamily{U}{wncy}{}
\DeclareFontShape{U}{wncy}{m}{n}{<->wncyss10}{}
\DeclareSymbolFont{mcy}{U}{wncy}{m}{n}
\DeclareMathSymbol{\sh}{\mathord}{mcy}{"78} 
\DeclareMathOperator{\sha}{\sh}
\DeclareMathOperator{\tr}{Tr}

@@

The shuffle product $\sha$ on a pair of finite words is defined inductively as
\begin{align*}
\epsilon \sha s &= \{s\},\\
s \sha \epsilon &= \{s\},\\
as \sha bt &= a(s \sha bt) \cup b(as \sha t).
\end{align*}
Shuffle is associative, commutative, and distributes over arbitrary
joins.

\begin{lem}
$(\mathcal{P}((\Sigma\times\Sigma)^*), \cup, \cdot, \sha, \emptyset, \{\epsilon\})$ is a weak trioid.
\end{lem}

@@

>>>>

\DeclareFontFamily{U}{wncy}{}
\DeclareFontShape{U}{wncy}{m}{n}{<->wncyss10}{}
\DeclareSymbolFont{mcy}{U}{wncy}{m}{n}
\DeclareMathSymbol{\sh}{\mathord}{mcy}{"78} 
\DeclareMathOperator{\sha}{\sh}
\DeclareMathOperator{\tr}{Tr}
\DeclareMathOperator{\fin}{finite}

@@

As usual, the product of two languages X and Y over an alphabet
$\Sigma$ is defined as $XY = \{x\frown y.\; x \in X \land y \in Y\}$.
The language product is associative, and distributes over arbitrary
joins from both the left and the right. The shuffle $\sha$ on a pair
of finite words is defined inductively as
\begin{align*}
\epsilon \sha s &= \{s\},\\
s \sha \epsilon &= \{s\},\\
as \sha bt &= a(s \sha bt) \cup b(as \sha t),
\end{align*}
which is then lifted to languages X and Y as the shuffle product,
\begin{align*}
X \sha Y = \bigcup\{xs \sha ys.\; x \in X \land x \in Y\}.
\end{align*}
The shuffle product is associative, commutative, and distributes over
arbitrary joins. Both products share the same unit, $\{\epsilon\}$ and
zero, $\emptyset$. Therefore, $(\mathcal{P}(\Sigma)^*), \cup, \cdot,
\sha, \emptyset, \{\epsilon\})$ forms a weak trioid.

\begin{lem}
$(\mathcal{P}(\Sigma)^*), \cup, \cdot, \sha, \emptyset, \{\epsilon\})$ is a weak trioid.
\end{lem}

@@

\begin{center}
\begin{tikzpicture}[x=1cm,auto]
  \node [elem] (s12) {$\sigma_2$};
  \node [elem, above of=s12] (s11) {$\sigma_1$};
  \node [elem, below of=s12] (s13) {$\sigma_3$};
  \node [right of=s13, node distance=0.75cm] (r1) {};
  \node [below of=r1, node distance=0.5cm] (t4) {R};

  \node [elem, right of=s12, node distance=1.5cm] (i2) {$\sigma_2$};
  \node [elem, above of=i2] (i1) {$\sigma_1$};
  \node [elem, below of=i2] (i3) {$\sigma_3$};
  \node [right of=i3, node distance=0.75cm] (ri) {};
  \node [below of=ri, node distance=0.5cm] (ti) {V};

  \node [elem, right of=i2, node distance=1.5cm] (s22) {$\sigma_2$};
  \node [elem, above of=s22] (s21) {$\sigma_1$};
  \node [elem, below of=s22] (s23) {$\sigma_3$};
  \node [right of=s23, node distance=0.75cm] (r2) {};
  \node [below of=r2, node distance=0.5cm] (t4) {S};

  \path [rel] (s11) -- (i1);
  \path [rel] (s21) -- (s32);
  \path [line] (s32) -- (s43);
  \path [line] (s43) -- (s52);
  \path [line] (i2) -- (s23);

  \path [rel] (s11) -- (i2);
  \path [line] (s12) -- (i2);
  \path [line] (s23) -- (s32);
  \path [line] (s32) -- (s42);
  \path [line] (s42) -- (s51);
  \path [rel] (s41) -- (s52);
\end{tikzpicture}
\end{center}
